---
title: "Lesson 3a In-class exercises"
author: "Magdalena Russell"
date: '2022-06-15'
output: html_document
---

__Under each heading below, type your code and run it. Feel free to add notes and comments to help you learn.__ 

# assign vector: 4 ages (50, 55, 60, 65)

```{r}
ages <- c(50, 55, 60, 65) 

```

# recall vector

```{r}
ages

```

What was returned?
A vector containing the ages 50, 55, 60, and 65

# how many things are in object?

```{r}
length(ages)

```


# what type of object?

```{r}
class(ages)

```

# get overview of object

```{r}
str(ages)

```


# performing functions on vectors

# calculate the mean or average

```{r}
mean(ages)

```

# get the minimum and maximum

```{r}
min(ages)
max(ages)

```

# create a vector of three body parts called `organs` 

```{r}
organs <- c("lungs", "heart", "brain")

```

# add a value to end of the vector called `organs`

```{r}
organs <- c(organs, "kidney")

```

# recall vector

```{r}
#run this code chunk
organs

```

What was returned?
A vector containing the four organs: lungs, heart, brain, kidney (in that order)


# add value at the beginning

```{r}
organs <- c("liver", organs)

```

# recall vector

```{r}
#run this code chunk
organs

```

What was returned?
A vector containing the five organs: liver, lungs, heart, brain, kidney (in that order)


# extracting second value

```{r}
organs[2]

```

# excluding second value

```{r}
organs[-2]

```

# separating numbers with commas does not work

```{r}
organs[2, 3]

```

# extracting first and third values

```{r}
organs[c(1, 3)]

```

# recall vector

```{r}
#run this code chunk
organs

```

What was returned?
The same vector as before (no changes)


# extracting the first 2 values:

```{r}
organs[1:2]

```
