---
title: "Lesson 4 Practice"
author: "Magdalena Russell"
date: '2022-06-15'
output: html_document
---

# Demo part 1: Working with dataframes!


# make a directory

```{r}
dir.create("data") # run me!
```



# download data from url

```{r}
download.file("https://raw.githubusercontent.com/magdalenarussell/cfc_curriculum/main/data/clinical.csv", "data/clinical.csv") # run me!
```



# import data and assign to object

```{r}
clinical <- read.csv("data/clinical.csv")      
```


# view data

```{r}
View(clinical)
```

# assess size of data frame

```{r}
dim(clinical)
```

# preview first few rows

```{r}
head(clinical)
```

# show last three rows
 
```{r}
tail(clinical, n = 3)
```

# view column names

```{r}
colnames(clinical)
```

# view row names

```{r}
rownames(clinical)
```

# show overview of object
 
```{r}
str(clinical)
```

# provide summary statistics for each column
 
```{r}
summary(clinical)
```

# Demo part 2


# extract first column and assign to a variable

```{r}
first_column <- clinical[1] 
```

# extract first column

```{r}
first_column_again <- clinical[, 1] 
```

# extract first row 

```{r}
first_row <- clinical[1, ] 
```

# extract cell from first row of first column

```{r}
single_cell <- clinical[1, 1] 
```

# extract a range of cells, rows 1 to 3, second column

```{r}
range_cells <- clinical[1:3, 2]
```

# exclude first column

```{r}
exclude_col <- clinical[, -1] 
```

# exclude first 100 rows

```{r}
exclude_range <- clinical[-c(1:100)] 
```

# extract column by name

```{r}
name_col1 <- clinical["sample_type"] 
```

# dollar sign syntax

```{r}
name_col4 <- clinical$sample_type        
```
