---
title: "Lesson 2 practice"
author: "Magdalena Russell"
date: '2022-06-15'
output: html_document
---

__Under each heading below, type your code and run it. Feel free to add notes and comments to help you learn.__ 

__We recommend typing out the code over copying and pasting as figuring out where you made mistakes is a normal and key part of coding! Talk to an instructor if you get stuck. :)__



# Basic math (type below this line)

```{r}
# This is a code chunk!
4 + 5

```

What is the answer? (be sure to run your code chunk) 
9

# Assigning value to an object

```{r}
weight_kg <- 10

```

# Recall object

```{r}
weight_kg

```

What was returned when you ran the previous code chunk?
10! The value I assigned previously


# Multiplication on an object (convert kg to lb)

```{r}
weight_kg * 2.2

```

# Assign weight conversion to object

```{r}
weight_lb <- weight_kg * 2.2 

```


# Reassign new value to an object

```{r}
weight_kg <- 100 


```

# Now, recall the `weight_kg` object

```{r}
weight_kg

```

What value was returned when you ran the above code chunk?

100! The original value was overwritten by the new value 

