---
title: "Lesson 3b Practice"
author: "Magdalena Russell"
date: '2022-06-15'
output: html_document
---

__Under each heading below, type your code and run it. Feel free to add notes and comments to help you learn.__ 

# assign vector: 4 ages (50, 55, 60, 65)

```{r}
# run this code chunk
ages <- c(50, 55, 60, 65)

```

# extracts values which meet condition

```{r}
ages[ages > 60] # run me!

```

What was the result?
A vector containing only 65

# extracts values numerically equivalent values

```{r}
ages[ages == 60] #run me!

```

What was the result?
A vector containing only 60

# ages less than 50 OR greater than 60

```{r}
ages[ages < 50 | ages > 60]
```

What was the result?
A vector containing 60

# ages greater than 50 AND less than 60

```{r}
ages[ages > 50 & ages < 60]
```

What was the result?
A vector containing only 55

# recall: extract values which meet condition

```{r}
ages[ages > 60] 

```


# negate and return the opposite

```{r}
ages[!(ages > 60)]
```

What was the result?
A vector containing 50 and 55


# create a vector with missing data

```{r}
heights <- c(2, 4, 4, NA, 6) # run me!

```

# calculate mean and max on vector with missing data

```{r}
mean(heights)
```

```{r}
max(heights)
```

# add argument to remove NA

```{r}
mean(heights, na.rm = TRUE)
```

What is the result now?
The actual mean/max

# identify elements which are missing data

```{r}
is.na(heights)
```

# reverse the TRUE/FALSE

# insert here, use the NOT logical operator

```{r}
!(is.na(heights))
```

# extract elements which are not missing values (not NAs)

```{r}
heights[!(is.na(heights))]
```

# assign to a new object

```{r}
heights_without_NA = heights[!(is.na(heights))] 

```

# see if mean can be calculated normally now

```{r}
#run me
mean(heights_without_NA)
```

What is the result? 


